Brief notes on erosion

### 2020-08-07 docs/proposals/NSF/PostDocs/Scope_of_work_FSU.tex
starting scope of work

\pagestyle{fancy}
\lhead{\footnotesize MNJ Moore}
\chead{\footnotesize Current and Pending Support}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}

\subsection*{Current Support:}

{\bf Title}: Dynamic interactions between fluid flows and moving boundaries \\
{\bf Source}: Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians \\
{\bf Total Award Amount:} \$42,000 (Travel funds only) \\
{\bf Duration:} September 1, 2017--August 31, 2022 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 0 \\

%\vspace{-17pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Pending Support:}

\noindent
{\bf Title}:  A Comprehensive Experimental And Computational Fluid Dynamics Analysis Of Coning In Non-Newtonian Tailings During Extraction From Tailings Ponds \\
{\bf Source}:  Institute for Oil Sands Innovation\\
{\bf Total Award Amount:} \$171,842 \\
{\bf Duration:}  January 1, 2020--January 1, 2022\\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 0 \\

\noindent
{\bf Title}: Erosion, Transport, and Dispersion in Granular and Porous
Media (this proposal) \\
{\bf Source}: National Science Foundation, Division of Mathematical
Sciences, Computational Mathematics \\
{\bf Total Award Amount:} \$439,824 \\ %\$439,193 \\
{\bf Duration:} July 1, 2020--June 30, 2023 \\
{\bf Person-Months Per Year Committed to Project:} Calendar: 0,
Academic: 0, Summer: 1 \\

>>>>

\pagestyle{fancy}
\lhead{\footnotesize Bryan D.~Quaife}
\chead{\footnotesize FSU Scope of Work}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}
\section*{Personnel}
The research at FSU will be performed by PI Quaife and Ph.D.~student
Jake Cherry for the duration of the award.

\section*{Deliverables}
\paragraph{Simulating mechanical and chemical erosion, as well as
transport, including sedimentation and compaction, of eroding bodies:}

\paragraph{Simulating the transport of finite Peclet number
concentrations in eroded porous medium.}

\paragraph{Improving numerical methods including fast summation methods,
preconditioners, and quadrature.}

\section*{Timeline}
